---
title: "Lab1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r Q1}
set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
              	   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))

summary(m)
```

Run the above code

# 1.From the model results:

## Extract the qr tolerance (tol).

```{r}

```

## Extract the term labels from the model.
hint: Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.

```{r}

```

# From the list

## Use at least two different methods to extract m.

```{r}


```

## Extract the third column of m. Maintain the dimensions (matrix structure).

```{r}

```

## Extract the score for student 7.

```{r}

```


# **Loops**

## 3.Use the “airquality” dataset, which is part of base R. Split it by Month
```{r}
aq <- (airquality)
by_month <- split(aq, aq$Month)
str(by_month)
```

## 4.Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)

```{r}

```
## 5.Replicate this calculation with lapply, sapply, and vapply

```{r}
lapply(by_month, function(x) mean(x$Ozone, na.rm=TRUE))

```

## 6.Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop).

```{r}

```

## 7.Use a for loop to save the plots to a folder on your computer

```{r}


```